Analysis

### 2022-05-09 manuscript/manuscript.Rmd
More misc stuff

Topologically Associating Domains (TADs) are formed via cohesin-mediated loop extrusion mechanism [@Alipour:2012aa][@Fudenberg:2016aa][@Goloborodko:2016vz][@Schwarzer:2016aa]. CTCF binding, especially in convergent orientation, has long been known to be critical for loop formation [@Dixon:2012aa].

@@

Chang et al. provides CTCF ChIP-seq peaks from mouse ESCs [@Chang:2021wl]. They report 174,268 peaks (83,522 unique regions) having at least one significant CTCF binding motif.

CTCFBSDB assembled predictred and experimentally detected CTCF binding information [@Bao:2008vq]. Human predictions containes 13,356 sites (hg19) and mouse predictions contained 5,504 sites (mm9).

>>>>

Topologically Associating Domains (TADs) are formed via cohesin-mediated loop extrusion mechanism [@Alipour:2012aa][@Fudenberg:2016aa][@Goloborodko:2016vz][@Schwarzer:2016aa]. CTCF binding, especially in convergent orientation, has long been known to be critical for loop formation [@Dixon:2012aa][@Oti:2016aa].

@@

Chang et al. provides CTCF ChIP-seq peaks from mouse ESCs [@Chang:2021wl]. They report 174,268 peaks (83,522 unique regions) having at least one significant CTCF binding motif (mm10 genome assembly).

CTCFBSDB assembled predicted and experimentally detected CTCF binding information [@Bao:2008vq]. Human predictions containes 13,356 sites and mouse predictions contained 5,504 sites (hg19 and mm9 genome assemblies, respectively). Unfortunately, the database has not been updated since 2012; therefore, its data is of limited use.
